Add Data

### 2025-07-09 data.qmd
Also mention OpenDP

[^anon-synth-tools]: For example, using [Amnesia](https://amnesia.openaire.eu/),
[ARX](https://arx.deidentifier.org/), [sdcTools](https://github.com/sdcTools),
or [Synthpop](https://www.synthpop.org.uk/).

>>>>

[^anon-synth-tools]: For example, using [Amnesia](https://amnesia.openaire.eu/),
[ARX](https://arx.deidentifier.org/), [sdcTools](https://github.com/sdcTools),
[Synthpop](https://www.synthpop.org.uk/), or [OpenDP](https://opendp.org/).
